Randomization and Traditional Examples using `okcupiddata` `profiles` data

### 2018-03-30 inst/doc/profiles_examples_both_methods.Rmd
Tweak vignettes

The `okcupiddata` is thought by some to be controversial. Its use here is only
to check for a variety of different variable types and levels. It will remain only in this
"cutting edge" version of the package as we continue to add and test examples.

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
#  generate(reps = 1000, type = "simulate") %>%
#  calculate(stat = "Chisq") %>% 
  visualize(method = "theoretical")
```

@@

## TO DO

### To Do (slope $t$ stat)
### To Do (Also overlay appropriate t distn)

<!-- ## Testing -->

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

One numerical variable (mean)

**Testing but not working yet**

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "t") %>% 
  visualize()
```

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>% 
  visualize()
```

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f") %>% 
  visualize()
```

### Currently testing t-stat
### To Do (Also overlay appropriate t distn)
### To Do (Shift t stats to be centered at 0 for bootstrapping)

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "t") %>% 
  visualize()
```

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(sex ~ city) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

@@

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

>>>>

There has been some recent [controversy](https://www.wired.com/2016/05/okcupid-study-reveals-perils-big-data-science/) surrounding data of this sort similar to what is given in the {okcupiddata} package. Explicit permission was obtained from OkCupid and usernames were not included in the data set for that package. Its use here is only
to check for a variety of different variable types and levels. It will remain only in this
"cutting edge" version of the package as we continue to add and test examples.

The `method = "both"` examples here do another randomization instead of using the one
with `visualize()` set to the default of `method = "randomization"`. This is to show the full
pipeline for a variety of examples, but more than likely you'll want to do something like the
following instead in practice.

```{r eval=FALSE}
null_distn <- prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("m", "f"))

null_distn %>% visualize()
null_distn %>% visualize(method = "both")
```

@@

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

@@

## Two numerical vars - SLR

Randomization approach to $t$-statistic

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t") %>% 
  visualize()
```

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t") %>% 
  visualize(method = "both")
```

# Determining whether or not to implement

Note that all code from here throughout the rest of this vignette is to think about but is not currently implemented

## One numerical variable (mean)

Randomization approach to $t$-statistic (Not implemented)

```{r eval=FALSE}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "t") %>% 
  visualize()
```

Theoretical distribution (Implemented)

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
#  generate(reps = 1000, type = "bootstrap") %>% 
#  calculate(stat = "t") %>% 
  visualize(method = "theoretical")
```

Overlay appropriate $t$ distribution on top of permuted t-statistics (Not implemented)

```{r eval=FALSE}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "t") %>% 
  visualize(method = "both")
```

@@

```{r eval=FALSE}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>% 
  visualize()
```

@@

```{r eval=FALSE}
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f") %>% 
  visualize()
```

### To Do (Also overlay appropriate t distn)
### To Do (Shift t stats to be centered at 0 for bootstrapping)

@@

```{r eval=FALSE}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "t") %>% 
  visualize()
```

@@

```{r eval=FALSE}
prof_small %>%
  specify(sex ~ city) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

@@

```{r eval=FALSE}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "slope") %>% 
  visualize()
```
